---
title: "script_to_text"
author: "Irene Morse"
date: "2023-07-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In a recent project I needed to write some scripts for videos that were going to be recorded and included as part of a [MOOC](https://en.wikipedia.org/wiki/Massive_open_online_course).

The good news was that the MOOC developer already had delivered some Zoom lectures that more-or-less covered the topics for the scripts.

The bad news was that the Zoom scripts were in .srt format with the text divided up into time chunks.

This was a rare case where I wanted to go from more information to less information, i.e. get rid of the time chunks and .srt formatting and convert everything into a more readable and editable blob of text.

This blob of text would give me an easy starting point for creating a more polished script that could be used in the MOOC.

## The Code

First we read in and inspect the .srt file.

```{r}
# read in
script_raw <- readLines('C:/Users/irene/Documents/GitHub/ISM_Portfolio/docs/script_to_text/GMT20230719-185150_Recording.transcript.vtt')
# inspect
head(script_raw, 9)
```

Next we create a function that will perform some basic text manipulations.

```{r}
script_to_blob <- function(script, one_speaker=TRUE){
  # check for and remove title if there
  if(!(grepl("\\d\\d:\\d\\d:\\d\\d.\\d\\d\\d", script_raw[1]))){
  script_raw <- script_raw[-1]
  }
  # identify and remove empty lines
  script_raw <- script_raw[-which(grepl("^$", script_raw)==TRUE)]
  # identify and remove section numbers
  script_raw <- script_raw[-which(grepl("^\\d+$", script_raw)==TRUE)]
  # identify and remove timestamps
  script_raw <- script_raw[-which(grepl("\\d\\d:\\d\\d:\\d\\d.\\d\\d\\d", script_raw)==TRUE)]
  if(one_speaker==TRUE){
    # remove speaker's name
    script_raw <- gsub(".+: ", "", script_raw[1])
    # paste lines together into one coherent string
    blob <- paste(script_raw, collapse=" ")
  }else if(one_speaker==FALSE){
    # paste lines together with each line representing a new speaker
    blob <- paste(script_raw, collapse="\\n")
  }
  return(blob)
}
```

```{r}
script_text <- script_to_blob(script_raw, one_speaker = TRUE)
print(script_text)
```

Write out the text as a new file and it's now ready to edit in your word processor of choice! Voila!

```{r}
# write out
writeLines(script_text, 'C:/Users/irene/Documents/GitHub/ISM_Portfolio/docs/script_to_text/editable_script.txt')
```

## Planned Updates

Scripts come in a variety of formats. Eventually I'd like to create a more generalized function that can convert scripts of any user-specified format into text blobs, or perhaps that can convert scripts from one user-specified format into another.
